The Rockerverse: Packages and Applications for Containerization with R

### 2020-01-31 README.Rmd
use more suitable font for sticker

```{r hexSticker, message=TRUE, warning=FALSE, cache=TRUE, include=FALSE}
if(!file.exists("rockerverse.png")) {
  library("magick")
  library("here")

  # https://commons.wikimedia.org/wiki/File:NASA-HS201427a-HubbleUltraDeepField2014-20140603.jpg
  universe <- magick::image_read("https://upload.wikimedia.org/wikipedia/commons/6/69/NASA-HS201427a-HubbleUltraDeepField2014-20140603.jpg")
  magick::image_write(universe, here("universe.png"))
  # rockerLogoMask <-
  magick::image_read("https://avatars2.githubusercontent.com/u/9100160?s=200&v=4") %>%
    magick::image_scale("2100x2100") %>%
    magick::image_channel("Matte") %>%
    image_negate() %>%
    magick::image_border("black", "150x0") %>%
    magick::image_write(here("rocker_mask.png"))

@@

  library("hexSticker")
  hexSticker::sticker(here("whaleverse.png"), package = "Rockerverse",
          p_size = 20, s_x = 0.97, s_y = 0.95, s_width = 1,
          h_fill = "#000000", h_color = "#ffffff",
          url = "github.com/nuest/rockerverse-paper",
          u_color = "#ffffff", u_size = 4,
          filename = here("rockerverse.png"))

  file.remove(c(here("universe.png"), here("whaleverse.png"), here("rocker_mask.png")))
}
```

@@

>>>>

```{r hexSticker, message=TRUE, warning=FALSE, cache=TRUE, include=FALSE}
library("magick")
library("here")

# https://commons.wikimedia.org/wiki/File:NASA-HS201427a-HubbleUltraDeepField2014-20140603.jpg
if(!file.exists("universe.png")) {
  universe <- magick::image_read("https://upload.wikimedia.org/wikipedia/commons/6/69/NASA-HS201427a-HubbleUltraDeepField2014-20140603.jpg")
  magick::image_write(universe, here("universe.png"))
}

magick::image_read("https://avatars2.githubusercontent.com/u/9100160?s=200&v=4") %>%
  magick::image_scale("2100x2100") %>%
  magick::image_channel("Matte") %>%
  image_negate() %>%
  magick::image_border("black", "150x0") %>%
  magick::image_write(here("rocker_mask.png"))

@@

library("sysfonts")
if(!file.exists(here::here("FinalFrontierOldStyle-8Pg.ttf"))) {
  stop("Download font Final Frontier Old Style, e.g. from https://www.fontspace.com/allen-r-walden/final-frontier-old-style and put the file in the repo root.")
}
sysfonts::font_add("finalfrontier", here::here("FinalFrontierOldStyle-8Pg.ttf"))

library("hexSticker")
hexSticker::sticker(here::here("whaleverse.png"), package = "ROCKERVERSE",
        p_family = "finalfrontier",
        p_size = 29, p_y = 1.3,
        s_x = 0.97, s_y = 0.95, s_width = 1,
        h_fill = "#000000", h_color = "#ffffff",
        url = "github.com/nuest/rockerverse-paper",
        u_color = "#ffffff", u_size = 4,
        filename = here::here("rockerverse.png"))

#file.remove(c(here("universe.png"), here("whaleverse.png"), here("rocker_mask.png")))
```

@@

Hex sticker uses the font [Final Frontier Old Style](https://www.fontspace.com/allen-r-walden/final-frontier-old-style) and the [Hubble Ultra-Deep Field](https://en.wikipedia.org/wiki/Hubble_Ultra-Deep_Field) combined with the Docker logo as background.
